Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-15 icse/paper.tex
Removed percentages

\begin{table}[H]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Category}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
\rowcolor[HTML]{FFCCC9}
Common Hierarchy & 0,63 & 27 \\
Sibling & 0,53 & 664 \\
No Direct Superclass & 0,11 & 295 \\
Same Method & 0,06 & 740 \\
\rowcolor[HTML]{FFCCC9}
Superclass & 0,03 & 68 \\
Same Class & 0,02 & 1273 \\
External Superclass & 0,01 & 209 \\
\rowcolor[HTML]{FFCCC9}
No Indirect Superclass & -0,06 & 36 \\
Same Interface & -0,07 & 269 \\
\rowcolor[HTML]{FFCCC9}
First Cousin & -0,19 & 54 \\
External Ancestor & -0,28 & 154 \\
\rowcolor[HTML]{FFCCC9}
Ancestor & -0,52 & 5 \\ \bottomrule
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}

>>>>

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Relation}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Maintainability\\ Score\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Number of\\ Refactorings\end{tabular}}} \\ \midrule
\textbf{Common Hierarchy} & \textbf{0,51} & \textbf{792} \\ \midrule
\hspace{10pt} Sibling & 0.57 & 637 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Same Hierarchy & 0,55 & 22 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Superclass & 0,20 & 74 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} First Cousin & -0,02 & 53 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Ancestor & -0,65 & 6 \\ \midrule
\textbf{Common Class} & \textbf{0,01} & \textbf{2025}\\ \midrule
\hspace{10pt} Same Method & 0,01 & 762  \\
\hspace{10pt} Same Class & 0,01 & 1263 \\ \midrule
\textbf{Unrelated} & \textbf{-0,02} & \textbf{688}\\ \midrule
\hspace{10pt} No Direct Superclass & 0,08 & 289 \\
\hspace{10pt} External Superclass & -0,02 & 225  \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} No Indirect Superclass & -0,04 & 30  \\
\hspace{10pt} External Ancestor & -0,26 & 144  \\ \midrule
\textbf{Common Interface} & \textbf{-0,11} & \textbf{283} \\ \midrule
\hspace{10pt} Same Direct Interface & 0,02 & 160 \\
\hspace{10pt} Same Indirect Interface & -0,31 & 123
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}
